\textbf{quicR}:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-05-28 man/manuscript/softwareX_submission.tex
Added a Reproducibility section.

>>>>

        \subsection{Reproducibility}
            To promote transparency and reproducibility, we provide a standardized benchmarking and data extraction script alongside the \textbf{quicR} package. This script processes raw RT-QuIC output files in MARS export format, computes key kinetic metrics (MPR, MS, TtT, RAF), and writes all intermediate and final results to CSV files. Users are instructed to run the script locally, generating three files (\texttt{<user>\_meta.csv}, \texttt{<user>\_data.csv}, and \texttt{<user>\_calcs.csv}) which were then compared across systems or submissions to ensure consistent performance.

            To further guard against system-dependent variability, the script includes the following measures:

            \begin{enumerate}
                % \item Sorting of input and output data by sample ID to enforce deterministic row order;
                \item Cross-platform user ID resolution to enable standardized filenames
                \item Fixed random seed initialization to control for any stochastic components
                \item Output of full session metadata via \texttt{sessionInfo()} to record package versions and platform details
                \item UTF-8 encoding of all CSV files for consistent parsing across operating systems.
            \end{enumerate}

            This reproducibility framework ensures that benchmark results, as reported in Table~\ref{tbl:benchmark}, can be independently validated and extended. The script, along with example data, is included in the package repository and supplementary materials.
